Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-08 article.tex
add : maccro \n modification : typo

@@

			\begin{proof}
			We consider the following problem :\\

			Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[\min,\max]\\

@@

			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

			\textbf{BASE :} \\

			if $n_\pmotif \notin  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

			if $n_\pmotif \notin  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						and }\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						and }\\
						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $\min<\ptext[j]<\max$} \\		
						&\\

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\

@@

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]+1]) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]-1]) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
						&\\

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

>>>>

%Pattern Marching

\DeclareMathOperator{\PMa}{PM}
\newcommand{\PM}[6]{\PMa_{{#1}}^{{#2},{#3},{#4}}({#5},{#6})}

@@

\begin{proof}
We consider the following problem :\\
Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

%$
%\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= 
%\begin{cases}
%true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$ with every element in $[\min,\max]$} \\
%false & otherwise
%\end{cases}
%$

$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\left\{ 
\begin{array}{l l}
	true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
		& \text{with every element in}\\ 
		&[\min,\max]\\

@@

$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction. 
it can be solved by means of the following relations:\\

\textbf{BASE :} \\
if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\	
$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}	
= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[j]<\max$}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
\\

if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\		
$ \PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[n_\ptext]<\max$}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
\\

if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[j]<\max$ and }\\
					&\text{$\ptext[j]$ is the maximal element}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[n_\ptext]<\max$and }\\
					&\text{$\ptext[n_\ptext]$ is the maximal element}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

\textbf{STEP :} \\		
$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}= \\ \left\{ 
		\begin{array}{l l}

			\bigcup_{j<k}
			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{k}
				& \text{if $\stripe{\pmotif}{i}=\ustep$
				and $i \notin \x$}\\
				& \text{and $i \notin \y$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\

			\bigcup_{j<k}
			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{k}
				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
				& \text{and $i \notin \x$ and $i \notin \y$  }\\
				& \text{and $\min<\ptext[j]<\max$} \\		
			&\\

			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}	
				& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
				& \text{and $i \in \x$ and $i \notin \y$}\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\

			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1} 
				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
				& \text{and $i \in \x$ and $i \notin \y$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\

@@

			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{\ptext^{-1}[\ptext[j]+1]} 
				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
				&\text{and $i \notin \x$ and $i \in \y$}\\
				& \text{and $\min<\ptext[j]<\max$} \\
				&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
			&\\

			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{\ptext^{-1}[\ptext[j]-1]} 	
				&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
				&\text{and $i \notin \x$ and $i \in \y$ }\\	
				& \text{and $\min<\ptext[j]<\max$} \\
				&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
			&\\

			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1} 
				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
				&\text{and $i \in \x$ and $i \in \y$}\\ 
				&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\

			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1} 
				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
				&\text{and $i \in \x$ and $i \in \y$}\\ 
				&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\	
			False & Otherwise\\																		
		\end{array} \right. $\\
